---
title: "Lab 00 - Hello IDS!"
author: "INSERT YOUR NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Lucy", "Zazzie", "Gabriel", 
           "Jin", "Alex", "Joel"),
  github_username = c("roydsle", "zarinakjellberg", "gamgow", 
                      "jin2226", "alexjdlr", "joelhanloned"), 
  colour = c("darkgreen", "blue", "pink", 
             "violet", "red", "green"),
  hobby = c("reading", "netball", "jazz trumpet", 
            "reading", "music", "drums"),
  favourite_number = c(7, 2, 2, 4, 10, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


For each username, the graph shows through the height of the bar the favourite number, and through colour, the favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "number",
          title = "practice graph")
```

The lab() function adds and allows edits to labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

After discussion, an itemised list was posed as a way to convey data, however the sheer number of discrete variables created a problem for conveyance of information.
